{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-31 brains-protocol.tex
Add an example in 4.2

>>>>

To make things concrete, here is an example substitution taking place in the dataset.
At the end of December 2008, many science-related websites reported the following quote,

\begin{quote}
    ``It could be that our emotions and the systems to regulate them are vestiges of our evolutionary ancestry.''
\end{quote}
and a minority of other websites reported the following,
\begin{quote}
    ``It could be that our emotions and the systems to regulate them are vestiges of our evolutionary \textbf{history}.''
\end{quote}
The word \emph{ancestry} is acquired at an average of 10.11 years old, appears about 12 times in the dataset, and (unfortunately) is not encoded in Free Association norms, meaning we have no Clustering coefficient for this word.
The word it was replaced with, \emph{history}, is acquired on average at 6.42 years old, appears about 33k times in the dataset, and has a Clustering coefficient of 0.1.
Such a change, though minor in appearance, is a typical example of alteration along the lines shown by our results.

%ancestry (age 10.11, phonemes 8.0, freq 2.48, cc -, susceptibility 1.0)
%history  [age 6.42, phonemes 6.0, freq 10.42, cc -2.30, susceptibility 0.0]
